---
title: "FaceNewsIntervention - Data Analysis"
editor: source
editor_options: 
  chunk_output_type: console
format:
  html:
    code-fold: true
    self-contained: true
    toc: true
---

## Data Preparation

```{r}
#| message: false
#| warning: false

library(emmeans)
library(tidyverse)
library(easystats)
library(patchwork)
library(ggside)
```

```{r}
#| code-fold: false

df <- read.csv("../data/data.csv") %>% 
  mutate(Intervention = as.factor(Intervention))
dfmist <- read.csv("../data/data_mist.csv") %>% 
  mutate(Condition = fct_relevel(Condition, "Pretest", "Posttest"))
dfmocri <- read.csv("../data/data_mocri.csv")

```



## Examples

::: {.panel-tabset}

### Example for Continuous Variable

```{r}

m <- lm(MIST_correct_Pretest_covid ~ poly(Political_LiberalConservative, 2), 
        data=filter(df, !is.na(Political_LiberalConservative)))

display(parameters(m))

estimate_relation(m, length=30) |> 
  ggplot(aes(x=Political_LiberalConservative, y=Predicted)) +
  # geom_jitter(data=filter(df, !is.na(Political_LiberalConservative)), 
  #             aes(y=MIST_correct_Pretest_covid), alpha=0.2, size=3) +
  geom_ribbon(aes(ymin=CI_low, ymax=CI_high), alpha=0.2) +
  geom_line() +
  labs(y="MIST-Covid (% Correct Pretest)", x="Political Identification")
```

### Example for Categorical Variable

```{r}
# Categorical
m <- lm(MIST_correct_Pretest_covid ~ Political_Affiliation, 
        data=filter(df, Political_Affiliation != "None or Independent"))

display(estimate_contrasts(m, contrast="Political_Affiliation", p_adjust="none"))

estimate_means(m, by = c("Political_Affiliation")) |> 
  ggplot(aes(x=Political_Affiliation, y=Mean)) +
  geom_line(aes(group=1)) + 
  geom_pointrange(aes(ymin=CI_low, ymax=CI_high)) +
  labs(y="MIST-Covid (% Correct Pretest)", x="Political Affiliation")
```



### Example for Multivariate Model

```{r}
# model <- glmmTMB::glmmTMB(Correct ~ Intervention * Condition * Topic + (1|Participant) + (1|QuestionID), 
#                           data=dfmist, family=binomial())
# 
# model_means <- modelbased::estimate_means(model, by=c("Intervention", "Condition", "Topic"))
# 
# model_means |> 
#   mutate(Condition = fct_rev(Condition)) |> 
#   ggplot(aes(x=Condition, y=Probability, color=Intervention)) +
#   geom_line(aes(group=Intervention), position=position_dodge(width=0.1)) +
#   geom_pointrange(aes(ymin=CI_low, ymax=CI_high), position=position_dodge(width=0.1)) +
#   facet_wrap(~Topic)
```

::: 

## MIST difference vs pre-test

::: {.panel-tabset}

### %Correct difference Post-Pre & %Correct Pretest

```{r}
df <- df %>%
  mutate(MIST_correct_Pretest_avg = (MIST_correct_Pretest_covid + MIST_correct_Pretest_general) / 2)


m <- lm(MIST_correct_Diff ~ Intervention / MIST_correct_Pretest_avg, 
        data = filter(df, !is.na(MIST_correct_Pretest_covid) & !is.na(MIST_correct_Pretest_general)))


display(parameters(m))

estimate_relation(m, length=30) |> 
  ggplot(aes(x=MIST_correct_Pretest_avg, y=Predicted)) +
  # geom_jitter(data=filter(df, !is.na(Political_LiberalConservative)), 
  #             aes(y=MIST_correct_Pretest_covid), alpha=0.2, size=3) +
  geom_ribbon(aes(ymin=CI_low, ymax=CI_high, fill=Intervention), alpha=0.2) +
  geom_line(aes(color=Intervention)) +
  labs(x="MIST (% Correct pre-test)", y="MIST (% Correct difference Post-Pre)")

```


### COVID (%Correct difference Post-Pre) (independent/predictor) & COVID (%Correct Pretest)

```{r}
m <- lm(MIST_correct_Diff_covid ~ Intervention/MIST_correct_Pretest_covid, 
        data=filter(df, !is.na(MIST_correct_Pretest_covid)))

display(parameters(m))

estimate_relation(m, length=30) |> 
  ggplot(aes(x=MIST_correct_Pretest_covid, y=Predicted)) +
  # geom_jitter(data=filter(df, !is.na(Political_LiberalConservative)), 
  #             aes(y=MIST_correct_Pretest_covid), alpha=0.2, size=3) +
  geom_ribbon(aes(ymin=CI_low, ymax=CI_high, fill=Intervention), alpha=0.2) +
  geom_line(aes(color=Intervention)) +
  labs(x="MIST COVID (% Correct pre-test)", y="MIST COVID (% Correct difference Post-Pre)")
```

### General (% Correct difference Post-Pre) (independent/predictor) & General (% Correct Pretest)

```{r}
m <- lm(MIST_correct_Diff_general ~ Intervention/MIST_correct_Pretest_general, 
        data=filter(df, !is.na(MIST_correct_Pretest_general)))

display(parameters(m))

estimate_relation(m, length=30) |> 
  ggplot(aes(x=MIST_correct_Pretest_general, y=Predicted)) +
  # geom_jitter(data=filter(df, !is.na(Political_LiberalConservative)), 
  #             aes(y=MIST_correct_Pretest_covid), alpha=0.2, size=3) +
  geom_ribbon(aes(ymin=CI_low, ymax=CI_high, fill=Intervention), alpha=0.2) +
  geom_line(aes(colour=Intervention)) +
  labs(x="MIST General (% Correct pre-test)", y="MIST General (% Correct difference Post-Pre)")
```

:::

## Gender

::: {.panel-tabset}


### MIST (dprime difference post-pre)

```{r}
# Categorical
df$Gender <- as.factor(df$Gender)
m <- lm(MIST_dprime_Diff ~ Gender, 
        data=filter(df, Gender != "Non-Binary" & Gender != "Prefer not to answer"))


display(estimate_contrasts(m, contrast="Gender", p_adjust="none"))

estimate_means(m, by = c("Gender")) |> 
  ggplot(aes(x=Gender, y=Mean)) +
  geom_line(aes(group=1)) + 
  geom_pointrange(aes(ymin=CI_low, ymax=CI_high)) +
  labs(y="MIST (dprime difference post-pre)", x="Gender")
```


::: 

## Education

::: {.panel-tabset}

### Education (independent/predictor) & MIST (dprime difference post-pre) (dependent/outcome)

```{r}
# Categorical
df$Education <- as.factor(df$Education)
df <- df %>% filter(!is.na(Education))
unique(trimws(df$Education))

m <- lm(MIST_dprime_Diff ~ Education, 
        data=filter(df, Education != "Other"))

display(estimate_contrasts(m, contrast="Education", p_adjust="none"))

estimate_means(m, by = c("Education")) |> 
  ggplot(aes(x=Education, y=Mean)) +
  geom_line(aes(group=1)) + 
  geom_pointrange(aes(ymin=CI_low, ymax=CI_high)) +
  labs(y="MIST (dprime difference post-pre)", x="Education")
```

::: 

## Age

::: {.panel-tabset}

### Age (independent/predictor) & MIST (dprime difference post-pre) (dependent/outcome)



```{r}
m <- lm(MIST_dprime_Diff ~ Age, 
        data=df)

display(parameters(m))

estimate_relation(m, length=30) |> 
  ggplot(aes(x=Age, y=Predicted)) +
  # geom_jitter(data=filter(df, !is.na(Political_LiberalConservative)), 
  #             aes(y=MIST_correct_Pretest_covid), alpha=0.2, size=3) +
  geom_ribbon(aes(ymin=CI_low, ymax=CI_high), alpha=0.2) +
  geom_line() +
  labs(y="MIST (dprime difference post-pre)", x="Age")
```

:::
## Intervention vs Control
::: {.panel-tabset}



### Intervention vs Control (independent/predictor) & MOCRI (% dprime difference post-pre) (dependent/outcome)

```{r}
# Categorical
m <- lm(MOCRI_dprime_Diff ~ Intervention, 
        data=df)

display(estimate_contrasts(m, contrast="Intervention", p_adjust="none"))

estimate_means(m, by = "Intervention") |> 
  ggplot(aes(x=Intervention, y=Mean)) +
  geom_line(aes(group=1)) + 
  geom_pointrange(aes(ymin=CI_low, ymax=CI_high)) +
  labs(y="MOCRI (% dprime difference post-pre)", x="Intervention vs Control")
```


### *Intervention vs Control (independent/predictor) & MIST COVID (dprime difference post-pre) (dependent/outcome)

```{r}
# Categorical
m <- lm(MIST_dprime_Diff_covid ~ Intervention, 
        data=df)

display(estimate_contrasts(m, contrast="Intervention", p_adjust="none"))

estimate_means(m, by = "Intervention") |> 
  ggplot(aes(x=Intervention, y=Mean)) +
  geom_line(aes(group=1)) + 
  geom_pointrange(aes(ymin=CI_low, ymax=CI_high)) +
  labs(y="MIST-Covid (dprime difference post-pre)", x="Intervention vs Control")
```


### *Intervention vs Control (independent/predictor) & MIST general (dprime difference post-pre) (dependent/outcome)

```{r}
# Categorical
m <- lm(MIST_dprime_Diff_general ~ Intervention, 
        data=df)

display(estimate_contrasts(m, contrast="Intervention", p_adjust="none"))

estimate_means(m, by = "Intervention") |> 
  ggplot(aes(x=Intervention, y=Mean)) +
  geom_line(aes(group=1)) + 
  geom_pointrange(aes(ymin=CI_low, ymax=CI_high)) +
  labs(y="MIST-general (dprime difference post-pre)", x="Intervention vs Control")
```

### *Intervention vs Control (independent/predictor) & MIST total (dprime difference post-pre) (dependent/outcome)

```{r}
# Categorical
m <- lm(MIST_dprime_Diff ~ Intervention, 
        data=df)

display(estimate_contrasts(m, contrast="Intervention", p_adjust="none"))

estimate_means(m, by = "Intervention") |> 
  ggplot(aes(x=Intervention, y=Mean)) +
  geom_line(aes(group=1)) + 
  geom_pointrange(aes(ymin=CI_low, ymax=CI_high)) +
  labs(y="MIST-TOTAL (dprime difference post-pre)", x="Intervention vs Control")
```
:::

## Criterion
::: {.panel-tabset}

###  Criterion MOCRI pretest (dependent/outcome) & Intervention vs Control (independent/predictor)

```{r}
# Categorical
m <- lm(MOCRI_criterion_Pre ~ Intervention, 
        data=df)

display(estimate_contrasts(m, contrast="Intervention", p_adjust="none"))

estimate_means(m, by = "Intervention") |> 
  ggplot(aes(x=Intervention, y=Mean)) +
  geom_line(aes(group=1)) + 
  geom_pointrange(aes(ymin=CI_low, ymax=CI_high)) +
  labs(y="MOCRI Criterion pretest", x="Intervention vs Control")
```

###  Criterion MOCRI posttest (dependent/outcome) & Intervention vs Control (independent/predictor)

```{r}
# Categorical
m <- lm(MOCRI_criterion_Post ~ Intervention, 
        data=df)

display(estimate_contrasts(m, contrast="Intervention", p_adjust="none"))

estimate_means(m, by = "Intervention") |> 
  ggplot(aes(x=Intervention, y=Mean)) +
  geom_line(aes(group=1)) + 
  geom_pointrange(aes(ymin=CI_low, ymax=CI_high)) +
  labs(y="MOCRI Criterion posttest", x="Intervention vs Control")
```

###  Criterion MOCRI difference post-pre (dependent/outcome) & Intervention vs Control (independent/predictor)

```{r}
# Categorical
m <- lm((MOCRI_criterion_Post-MOCRI_criterion_Pre) ~ Intervention, 
        data=df)

display(estimate_contrasts(m, contrast="Intervention", p_adjust="none"))

estimate_means(m, by = "Intervention") |> 
  ggplot(aes(x=Intervention, y=Mean)) +
  geom_line(aes(group=1)) + 
  geom_pointrange(aes(ymin=CI_low, ymax=CI_high)) +
  labs(y="Criterion MOCRI difference post-pre", x="Intervention vs Control")
```


###  Criterion MIST pretest COVID (dependent/outcome) & Intervention vs Control (independent/predictor)

```{r}
# Categorical
m <- lm(MIST_criterion_Pretest_covid ~ Intervention, 
        data=df)

display(estimate_contrasts(m, contrast="Intervention", p_adjust="none"))

estimate_means(m, by = "Intervention") |> 
  ggplot(aes(x=Intervention, y=Mean)) +
  geom_line(aes(group=1)) + 
  geom_pointrange(aes(ymin=CI_low, ymax=CI_high)) +
  labs(y="MIST Criterion pretest COVID", x="Intervention vs Control")
```

###  Criterion MIST pretest GENERAL (dependent/outcome) & Intervention vs Control (independent/predictor)

```{r}
# Categorical
m <- lm(MIST_criterion_Pretest_general ~ Intervention, 
        data=df)

display(estimate_contrasts(m, contrast="Intervention", p_adjust="none"))

estimate_means(m, by = "Intervention") |> 
  ggplot(aes(x=Intervention, y=Mean)) +
  geom_line(aes(group=1)) + 
  geom_pointrange(aes(ymin=CI_low, ymax=CI_high)) +
  labs(y="MIST Criterion pretest GENERAL", x="Intervention vs Control")
```

###  Criterion MIST posttest COVID (dependent/outcome) & Intervention vs Control (independent/predictor)

```{r}
# Categorical
m <- lm(MIST_criterion_Posttest_covid ~ Intervention, 
        data=df)

display(estimate_contrasts(m, contrast="Intervention", p_adjust="none"))

estimate_means(m, by = "Intervention") |> 
  ggplot(aes(x=Intervention, y=Mean)) +
  geom_line(aes(group=1)) + 
  geom_pointrange(aes(ymin=CI_low, ymax=CI_high)) +
  labs(y="MIST Criterion posttest COVID", x="Intervention vs Control")
```

###  Criterion MIST posttest GENERAL (dependent/outcome) & Intervention vs Control (independent/predictor)

```{r}
# Categorical
m <- lm(MIST_criterion_Posttest_general ~ Intervention, 
        data=df)

display(estimate_contrasts(m, contrast="Intervention", p_adjust="none"))

estimate_means(m, by = "Intervention") |> 
  ggplot(aes(x=Intervention, y=Mean)) +
  geom_line(aes(group=1)) + 
  geom_pointrange(aes(ymin=CI_low, ymax=CI_high)) +
  labs(y="MIST Criterion posttest GENERAL", x="Intervention vs Control")
```

###  Criterion MIST difference post-pre COVID (dependent/outcome) & Intervention vs Control (independent/predictor)

```{r}
# Categorical
m <- lm(MIST_criterion_Diff_covid ~ Intervention, 
        data=df)

display(estimate_contrasts(m, contrast="Intervention", p_adjust="none"))

estimate_means(m, by = "Intervention") |> 
  ggplot(aes(x=Intervention, y=Mean)) +
  geom_line(aes(group=1)) + 
  geom_pointrange(aes(ymin=CI_low, ymax=CI_high)) +
  labs(y="Criterion MIST difference post-pre COVID", x="Intervention vs Control")
```

###  *Criterion MIST difference post-pre GENERAL (dependent/outcome) & Intervention vs Control (independent/predictor)

```{r}
# Categorical
m <- lm(MIST_criterion_Diff_general ~ Intervention, 
        data=df)

display(estimate_contrasts(m, contrast="Intervention", p_adjust="none"))

estimate_means(m, by = "Intervention") |> 
  ggplot(aes(x=Intervention, y=Mean)) +
  geom_line(aes(group=1)) + 
  geom_pointrange(aes(ymin=CI_low, ymax=CI_high)) +
  labs(y="Criterion MIST difference post-pre GENERAL", x="Intervention vs Control")
```

###  Criterion MIST difference post-pre OVERALL (dependent/outcome) & Intervention vs Control (independent/predictor)

```{r}
# Categorical
m <- lm((MIST_criterion_Diff_general + MIST_criterion_Diff_covid)/2 ~ Intervention, 
        data=df)

display(estimate_contrasts(m, contrast="Intervention", p_adjust="none"))

estimate_means(m, by = "Intervention") |> 
  ggplot(aes(x=Intervention, y=Mean)) +
  geom_line(aes(group=1)) + 
  geom_pointrange(aes(ymin=CI_low, ymax=CI_high)) +
  labs(y="Criterion MIST difference post-pre OVERALL", x="Intervention vs Control")
```

### Criterion MIST difference post-pre GENERAL (dependent/outcome) & MIST general (dprime difference post-pre) (independent/predictor)
<!-- trying here to look at dprime vs criterion for the most meaningful significant differene found in both dprime and criterion, but not sure what is causing the error in running here -->

```{r}
# m <- lm(MIST_criterion_Diff_general ~ Intervention/MIST_dprime_Diff_general,
#         data=filter(df, ))
# 
# display(parameters(m))
# 
# estimate_relation(m, length=30) |>
#   ggplot(aes(x=dprime, y=criterion)) +
#   # geom_jitter(data=filter(df, !is.na(Political_LiberalConservative)),
#   #             aes(y=MIST_correct_Pretest_covid), alpha=0.2, size=3) +
#   geom_ribbon(aes(ymin=CI_low, ymax=CI_high, fill=Intervention), alpha=0.2) +
#   geom_line(aes(colour=Intervention)) +
#   labs(y="MIST General (criterion difference Pre-test)", x="MIST General (dprime difference post-pre)")
```

:::
## Confidence
::: {.panel-tabset}

###  *Confidence MIST pretest FAKE GENERAL (dependent/outcome) & Intervention vs Control (independent/predictor)

```{r}
# Categorical
m <- lm(MIST_Confidence_Pretest_fake_general ~ Intervention, 
        data=df)

display(estimate_contrasts(m, contrast="Intervention", p_adjust="none"))

estimate_means(m, by = "Intervention") |> 
  ggplot(aes(x=Intervention, y=Mean)) +
  geom_line(aes(group=1)) + 
  geom_pointrange(aes(ymin=CI_low, ymax=CI_high)) +
  labs(y="Confidence MIST pretest FAKE GENERAL", x="Intervention vs Control")
```

###  Confidence MIST pretest FAKE COVID (dependent/outcome) & Intervention vs Control (independent/predictor)

```{r}
# Categorical
m <- lm(MIST_Confidence_Pretest_fake_covid ~ Intervention, 
        data=df)

display(estimate_contrasts(m, contrast="Intervention", p_adjust="none"))

estimate_means(m, by = "Intervention") |> 
  ggplot(aes(x=Intervention, y=Mean)) +
  geom_line(aes(group=1)) + 
  geom_pointrange(aes(ymin=CI_low, ymax=CI_high)) +
  labs(y="Confidence MIST pretest FAKE COVID", x="Intervention vs Control")
```

###  Confidence MIST pretest REAL GENERAL (dependent/outcome) & Intervention vs Control (independent/predictor)

```{r}
# Categorical
m <- lm(MIST_Confidence_Pretest_real_general ~ Intervention, 
        data=df)

display(estimate_contrasts(m, contrast="Intervention", p_adjust="none"))

estimate_means(m, by = "Intervention") |> 
  ggplot(aes(x=Intervention, y=Mean)) +
  geom_line(aes(group=1)) + 
  geom_pointrange(aes(ymin=CI_low, ymax=CI_high)) +
  labs(y="Confidence MIST pretest REAL GENERAL", x="Intervention vs Control")
```

###  Confidence MIST pretest REAL COVID (dependent/outcome) & Intervention vs Control (independent/predictor)

```{r}
# Categorical
m <- lm(MIST_Confidence_Pretest_real_covid ~ Intervention, 
        data=df)

display(estimate_contrasts(m, contrast="Intervention", p_adjust="none"))

estimate_means(m, by = "Intervention") |> 
  ggplot(aes(x=Intervention, y=Mean)) +
  geom_line(aes(group=1)) + 
  geom_pointrange(aes(ymin=CI_low, ymax=CI_high)) +
  labs(y="Confidence MIST pretest REAL COVID", x="Intervention vs Control")
```

###  Confidence MIST pretest overall (dependent/outcome) & Intervention vs Control (independent/predictor)

```{r}
# Categorical
m <- lm(MIST_Confidence_Pretest ~ Intervention, 
        data=df)

display(estimate_contrasts(m, contrast="Intervention", p_adjust="none"))

estimate_means(m, by = "Intervention") |> 
  ggplot(aes(x=Intervention, y=Mean)) +
  geom_line(aes(group=1)) + 
  geom_pointrange(aes(ymin=CI_low, ymax=CI_high)) +
  labs(y="Confidence MIST pretest overall", x="Intervention vs Control")
```


###  Confidence MIST posttest REAL GENERAL (dependent/outcome) & Intervention vs Control (independent/predictor)

```{r}
# Categorical
m <- lm(MIST_Confidence_Posttest_real_general ~ Intervention, 
        data=df)

display(estimate_contrasts(m, contrast="Intervention", p_adjust="none"))

estimate_means(m, by = "Intervention") |> 
  ggplot(aes(x=Intervention, y=Mean)) +
  geom_line(aes(group=1)) + 
  geom_pointrange(aes(ymin=CI_low, ymax=CI_high)) +
  labs(y="Confidence MIST posttest REAL GENERAL", x="Intervention vs Control")
```


###  Confidence MIST posttest FAKE GENERAL (dependent/outcome) & Intervention vs Control (independent/predictor)

```{r}
# Categorical
m <- lm(MIST_Confidence_Posttest_fake_general ~ Intervention, 
        data=df)

display(estimate_contrasts(m, contrast="Intervention", p_adjust="none"))

estimate_means(m, by = "Intervention") |> 
  ggplot(aes(x=Intervention, y=Mean)) +
  geom_line(aes(group=1)) + 
  geom_pointrange(aes(ymin=CI_low, ymax=CI_high)) +
  labs(y="Confidence MIST posttest FAKE GENERAL", x="Intervention vs Control")
```

###  Confidence MIST posttest REAL COVID (dependent/outcome) & Intervention vs Control (independent/predictor)

```{r}
# Categorical
m <- lm(MIST_Confidence_Posttest_real_covid ~ Intervention, 
        data=df)

display(estimate_contrasts(m, contrast="Intervention", p_adjust="none"))

estimate_means(m, by = "Intervention") |> 
  ggplot(aes(x=Intervention, y=Mean)) +
  geom_line(aes(group=1)) + 
  geom_pointrange(aes(ymin=CI_low, ymax=CI_high)) +
  labs(y="Confidence MIST posttest REAL COVID", x="Intervention vs Control")
```

###  Confidence MIST posttest FAKE COVID (dependent/outcome) & Intervention vs Control (independent/predictor)

```{r}
# Categorical
m <- lm(MIST_Confidence_Posttest_fake_covid ~ Intervention, 
        data=df)

display(estimate_contrasts(m, contrast="Intervention", p_adjust="none"))

estimate_means(m, by = "Intervention") |> 
  ggplot(aes(x=Intervention, y=Mean)) +
  geom_line(aes(group=1)) + 
  geom_pointrange(aes(ymin=CI_low, ymax=CI_high)) +
  labs(y="Confidence MIST posttest FAKE COVID", x="Intervention vs Control")
```

###  Confidence MIST posttest overall (dependent/outcome) & Intervention vs Control (independent/predictor)

```{r}
# Categorical
m <- lm(MIST_Confidence_Posttest ~ Intervention, 
        data=df)

display(estimate_contrasts(m, contrast="Intervention", p_adjust="none"))

estimate_means(m, by = "Intervention") |> 
  ggplot(aes(x=Intervention, y=Mean)) +
  geom_line(aes(group=1)) + 
  geom_pointrange(aes(ymin=CI_low, ymax=CI_high)) +
  labs(y="Confidence MIST posttest overall", x="Intervention vs Control")
```

###  *Confidence MIST difference post-pre (dependent/outcome) & Intervention vs Control (independent/predictor)

```{r}
# Categorical
m <- lm((MIST_Confidence_Posttest - MIST_Confidence_Pretest) ~ Intervention, 
        data=df)

display(estimate_contrasts(m, contrast="Intervention", p_adjust="none"))

estimate_means(m, by = "Intervention") |> 
  ggplot(aes(x=Intervention, y=Mean)) +
  geom_line(aes(group=1)) + 
  geom_pointrange(aes(ymin=CI_low, ymax=CI_high)) +
  labs(y="Confidence MIST difference post-pre", x="Intervention vs Control")
```



### *t-test intervention group ONLY, pretest vs posttest confidence

```{r}
# Subset the data for just the BadNews intervention group
df_badnews <- filter(df, Intervention == "BadNews")

# Paired t-test comparing pretest and posttest confidence
t.test(df_badnews$MIST_Confidence_Pretest, 
       df_badnews$MIST_Confidence_Posttest, 
       paired = TRUE)

```
:::
## Mixed Model

### Probability of being Correct

```{r}

model <- glmmTMB::glmmTMB(Correct ~ QuestionType / Topic  / (Condition * Intervention) + (1|Participant), data=dfmist, family="binomial")

# model <- rstanarm::stan_glmer(Correct ~ QuestionType / Topic  / (Condition * Intervention) + (1|Participant), data=dfmist, family="binomial")

estimate_relation(model) |> 
  ggplot(aes(x=Condition, y=Predicted)) +
  geom_line(aes(color=Intervention, group=Intervention)) + 
  geom_pointrange(aes(color=Intervention, ymin=CI_low, ymax=CI_high)) +
  facet_wrap(~QuestionType * Topic, scales="free")


estimate_contrasts(model, contrast=c("Condition"), by=c("Topic","Intervention"))

```

### Confidence


```{r}
dfmist$Confidence <- abs(datawizard::change_scale(dfmist$MIST, to=c(-1, 1), range = c(0, 100)))

model <- glmmTMB::glmmTMB(Confidence ~ Correct / QuestionType / Topic  / (Condition * Intervention) + (1|Participant), 
                          data=mutate(dfmist, Correct = ifelse(Correct == 1, "Correct", "Incorrect")))

estimate_relation(model) |> 
  ggplot(aes(x=Condition, y=Predicted)) +
  geom_line(aes(color=Intervention, group=Intervention)) + 
  geom_pointrange(aes(color=Intervention, ymin=CI_low, ymax=CI_high)) +
  facet_wrap(~Correct * QuestionType * Topic, scales="free")


estimate_contrasts(model, contrast=c("Condition"), by=c("Correct","Topic","Intervention"))

estimate_contrasts(model, contrast=c("Intervention"), by=c("Condition"))

estimate_contrasts(model, contrast=c("Intervention"), by=c("Correct","Topic","Condition"))
```