---
title: "FaceNewsIntervention - Data Analysis"
editor: source
editor_options: 
  chunk_output_type: console
format:
  html:
    code-fold: true
    self-contained: true
    toc: true
---


## Data Preparation

```{r}
#| message: false
#| warning: false

library(emmeans)
library(tidyverse)
library(easystats)
library(patchwork)
library(ggside)
```


```{r}
#| code-fold: false

df <- read.csv("../data/data.csv")
dfmist <- read.csv("../data/data_mist.csv")
```

## Analysis


### Example for Continuous Variable

```{r}

m <- lm(MIST_correct_Pretest_covid ~ poly(Political_LiberalConservative, 2), 
        data=filter(df, !is.na(Political_LiberalConservative)))

display(parameters(m))

estimate_relation(m, length=30) |> 
  ggplot(aes(x=Political_LiberalConservative, y=Predicted)) +
  # geom_jitter(data=filter(df, !is.na(Political_LiberalConservative)), 
  #             aes(y=MIST_correct_Pretest_covid), alpha=0.2, size=3) +
  geom_ribbon(aes(ymin=CI_low, ymax=CI_high), alpha=0.2) +
  geom_line() +
  labs(y="MIST-Covid (% Correct Pretest)", x="Political Identification")
```

### Example for Categorical Variable


```{r}
# Categorical
m <- lm(MIST_correct_Pretest_covid ~ Political_Affiliation, 
        data=filter(df, Political_Affiliation != "None or Independent"))

display(estimate_contrasts(m, contrast="Political_Affiliation", p_adjust="none"))

estimate_means(m, by = c("Political_Affiliation")) |> 
  ggplot(aes(x=Political_Affiliation, y=Mean)) +
  geom_line(aes(group=1)) + 
  geom_pointrange(aes(ymin=CI_low, ymax=CI_high)) +
  labs(y="MIST-Covid (% Correct Pretest)", x="Political Affiliation")
```

--------------------------------------------------------------------------

## Multivariate Model

```{r}
# model <- glmmTMB::glmmTMB(Correct ~ Intervention * Condition * Topic + (1|Participant) + (1|QuestionID), 
#                           data=dfmist, family=binomial())
# 
# model_means <- modelbased::estimate_means(model, by=c("Intervention", "Condition", "Topic"))
# 
# model_means |> 
#   mutate(Condition = fct_rev(Condition)) |> 
#   ggplot(aes(x=Condition, y=Probability, color=Intervention)) +
#   geom_line(aes(group=Intervention), position=position_dodge(width=0.1)) +
#   geom_pointrange(aes(ymin=CI_low, ymax=CI_high), position=position_dodge(width=0.1)) +
#   facet_wrap(~Topic)
```

--------------------------------------------------------------------------

## self-identified political ideology (independent/predictor) & VSA general score (dependent/outcome)

```{r}
m <- lm(VSA_General ~ poly(Political_LiberalConservative, 2), 
        data=filter(df, !is.na(Political_LiberalConservative)))

display(parameters(m))

estimate_relation(m, length=30) |> 
  ggplot(aes(x=Political_LiberalConservative, y=Predicted)) +
  # geom_jitter(data=filter(df, !is.na(Political_LiberalConservative)), 
  #             aes(y=MIST_correct_Pretest_covid), alpha=0.2, size=3) +
  geom_ribbon(aes(ymin=CI_low, ymax=CI_high), alpha=0.2) +
  geom_line() +
  labs(y="VSA General Mean Score", x="Political Identification")
```

## self-identified political ideology (independent/predictor) & VSA authoritarianism score (dependent/outcome)

```{r}
m <- lm(VSA_Authoritarianism ~ poly(Political_LiberalConservative, 2), 
        data=filter(df, !is.na(Political_LiberalConservative)))

display(parameters(m))

estimate_relation(m, length=30) |> 
  ggplot(aes(x=Political_LiberalConservative, y=Predicted)) +
  # geom_jitter(data=filter(df, !is.na(Political_LiberalConservative)), 
  #             aes(y=MIST_correct_Pretest_covid), alpha=0.2, size=3) +
  geom_ribbon(aes(ymin=CI_low, ymax=CI_high), alpha=0.2) +
  geom_line() +
  labs(y="VSA Authoritarianism Score", x="Political Identification")
```


## self-identified political ideology (independent/predictor) & BFI_Agreeableness (dependent/outcome)

```{r}
m <- lm(BFI_Agreeableness ~ poly(Political_LiberalConservative, 2), 
        data=filter(df, !is.na(Political_LiberalConservative)))

display(parameters(m))

estimate_relation(m, length=30) |> 
  ggplot(aes(x=Political_LiberalConservative, y=Predicted)) +
  # geom_jitter(data=filter(df, !is.na(Political_LiberalConservative)), 
  #             aes(y=MIST_correct_Pretest_covid), alpha=0.2, size=3) +
  geom_ribbon(aes(ymin=CI_low, ymax=CI_high), alpha=0.2) +
  geom_line() +
  labs(y="BFI Agreeableness", x="Political Identification")
```

## self-identified political ideology (independent/predictor) & BFI_Extraversion (dependent/outcome)

```{r}
m <- lm(BFI_Extraversion ~ poly(Political_LiberalConservative, 2), 
        data=filter(df, !is.na(Political_LiberalConservative)))

display(parameters(m))

estimate_relation(m, length=30) |> 
  ggplot(aes(x=Political_LiberalConservative, y=Predicted)) +
  # geom_jitter(data=filter(df, !is.na(Political_LiberalConservative)), 
  #             aes(y=MIST_correct_Pretest_covid), alpha=0.2, size=3) +
  geom_ribbon(aes(ymin=CI_low, ymax=CI_high), alpha=0.2) +
  geom_line() +
  labs(y="BFI Extraversion", x="Political Identification")
```

## self-identified political ideology (independent/predictor) & BFI_Conscientiousness (dependent/outcome)

```{r}
m <- lm(BFI_Conscientiousness ~ poly(Political_LiberalConservative, 2), 
        data=filter(df, !is.na(Political_LiberalConservative)))

display(parameters(m))

estimate_relation(m, length=30) |> 
  ggplot(aes(x=Political_LiberalConservative, y=Predicted)) +
  # geom_jitter(data=filter(df, !is.na(Political_LiberalConservative)), 
  #             aes(y=MIST_correct_Pretest_covid), alpha=0.2, size=3) +
  geom_ribbon(aes(ymin=CI_low, ymax=CI_high), alpha=0.2) +
  geom_line() +
  labs(y="BFI Conscientiousness", x="Political Identification")
```

## self-identified political ideology (independent/predictor) & BFI_Neuroticism (dependent/outcome)

```{r}
m <- lm(BFI_Neuroticism ~ poly(Political_LiberalConservative, 2), 
        data=filter(df, !is.na(Political_LiberalConservative)))

display(parameters(m))

estimate_relation(m, length=30) |> 
  ggplot(aes(x=Political_LiberalConservative, y=Predicted)) +
  # geom_jitter(data=filter(df, !is.na(Political_LiberalConservative)), 
  #             aes(y=MIST_correct_Pretest_covid), alpha=0.2, size=3) +
  geom_ribbon(aes(ymin=CI_low, ymax=CI_high), alpha=0.2) +
  geom_line() +
  labs(y="BFI_Neuroticism", x="Political Identification")
```

## self-identified political ideology (independent/predictor) & BFI_Openness (dependent/outcome)

```{r}
m <- lm(BFI_Openness ~ poly(Political_LiberalConservative, 2), 
        data=filter(df, !is.na(Political_LiberalConservative)))

display(parameters(m))

estimate_relation(m, length=30) |> 
  ggplot(aes(x=Political_LiberalConservative, y=Predicted)) +
  # geom_jitter(data=filter(df, !is.na(Political_LiberalConservative)), 
  #             aes(y=MIST_correct_Pretest_covid), alpha=0.2, size=3) +
  geom_ribbon(aes(ymin=CI_low, ymax=CI_high), alpha=0.2) +
  geom_line() +
  labs(y="BFI_Openness", x="Political Identification")
```

## self-identified political ideology (independent/predictor) & GCBS_General (dependent/outcome)

```{r}
m <- lm(GCBS_General ~ poly(Political_LiberalConservative, 2), 
        data=filter(df, !is.na(Political_LiberalConservative)))

display(parameters(m))

estimate_relation(m, length=30) |> 
  ggplot(aes(x=Political_LiberalConservative, y=Predicted)) +
  # geom_jitter(data=filter(df, !is.na(Political_LiberalConservative)), 
  #             aes(y=MIST_correct_Pretest_covid), alpha=0.2, size=3) +
  geom_ribbon(aes(ymin=CI_low, ymax=CI_high), alpha=0.2) +
  geom_line() +
  labs(y="GCBS_General", x="Political Identification")
```

## self-identified political ideology (independent/predictor) & GCBS_Control (dependent/outcome)

```{r}
m <- lm(GCBS_Control ~ poly(Political_LiberalConservative, 2), 
        data=filter(df, !is.na(Political_LiberalConservative)))

display(parameters(m))

estimate_relation(m, length=30) |> 
  ggplot(aes(x=Political_LiberalConservative, y=Predicted)) +
  # geom_jitter(data=filter(df, !is.na(Political_LiberalConservative)), 
  #             aes(y=MIST_correct_Pretest_covid), alpha=0.2, size=3) +
  geom_ribbon(aes(ymin=CI_low, ymax=CI_high), alpha=0.2) +
  geom_line() +
  labs(y="GCBS_Control", x="Political Identification")
```

## self-identified political ideology (independent/predictor) & GCBS_Wellbeing (dependent/outcome)

```{r}
m <- lm(GCBS_Wellbeing ~ poly(Political_LiberalConservative, 2), 
        data=filter(df, !is.na(Political_LiberalConservative)))

display(parameters(m))

estimate_relation(m, length=30) |> 
  ggplot(aes(x=Political_LiberalConservative, y=Predicted)) +
  # geom_jitter(data=filter(df, !is.na(Political_LiberalConservative)), 
  #             aes(y=MIST_correct_Pretest_covid), alpha=0.2, size=3) +
  geom_ribbon(aes(ymin=CI_low, ymax=CI_high), alpha=0.2) +
  geom_line() +
  labs(y="GCBS_Wellbeing", x="Political Identification")
```

## self-identified political ideology (independent/predictor) & GCBS_Malevolent (dependent/outcome)

```{r}
m <- lm(GCBS_Malevolent ~ poly(Political_LiberalConservative, 2), 
        data=filter(df, !is.na(Political_LiberalConservative)))

display(parameters(m))

estimate_relation(m, length=30) |> 
  ggplot(aes(x=Political_LiberalConservative, y=Predicted)) +
  # geom_jitter(data=filter(df, !is.na(Political_LiberalConservative)), 
  #             aes(y=MIST_correct_Pretest_covid), alpha=0.2, size=3) +
  geom_ribbon(aes(ymin=CI_low, ymax=CI_high), alpha=0.2) +
  geom_line() +
  labs(y="GCBS_Malevolent", x="Political Identification")
```

## self-identified political ideology (independent/predictor) & GCBS_Extraterrestrial (dependent/outcome)

```{r}
m <- lm(GCBS_Extraterrestrial ~ poly(Political_LiberalConservative, 2), 
        data=filter(df, !is.na(Political_LiberalConservative)))

display(parameters(m))

estimate_relation(m, length=30) |> 
  ggplot(aes(x=Political_LiberalConservative, y=Predicted)) +
  # geom_jitter(data=filter(df, !is.na(Political_LiberalConservative)), 
  #             aes(y=MIST_correct_Pretest_covid), alpha=0.2, size=3) +
  geom_ribbon(aes(ymin=CI_low, ymax=CI_high), alpha=0.2) +
  geom_line() +
  labs(y="GCBS_Extraterrestrial", x="Political Identification")
```

## self-identified political ideology (independent/predictor) & GCBS_GovernmentMalfeasance (dependent/outcome)

```{r}
m <- lm(GCBS_GovernmentMalfeasance ~ poly(Political_LiberalConservative, 2), 
        data=filter(df, !is.na(Political_LiberalConservative)))

display(parameters(m))

estimate_relation(m, length=30) |> 
  ggplot(aes(x=Political_LiberalConservative, y=Predicted)) +
  # geom_jitter(data=filter(df, !is.na(Political_LiberalConservative)), 
  #             aes(y=MIST_correct_Pretest_covid), alpha=0.2, size=3) +
  geom_ribbon(aes(ymin=CI_low, ymax=CI_high), alpha=0.2) +
  geom_line() +
  labs(y="GCBS_GovernmentMalfeasance", x="Political Identification")
```


## self-identified political ideology (independent/predictor) & MIST General (% Correct difference Post-Pre) (dependent/outcome)

```{r}
m <- lm(MIST_correct_Diff_general ~ poly(Political_LiberalConservative, 2), 
        data=filter(df, !is.na(Political_LiberalConservative)))

display(parameters(m))

estimate_relation(m, length=30) |> 
  ggplot(aes(x=Political_LiberalConservative, y=Predicted)) +
  # geom_jitter(data=filter(df, !is.na(Political_LiberalConservative)), 
  #             aes(y=MIST_correct_Pretest_covid), alpha=0.2, size=3) +
  geom_ribbon(aes(ymin=CI_low, ymax=CI_high), alpha=0.2) +
  geom_line() +
  labs(y="MIST General (% Correct difference Post-Pre)", x="Political Identification")
```


## self-identified political ideology (independent/predictor) & MIST COVID (% Correct difference Post-Pre) (dependent/outcome)

```{r}
m <- lm(MIST_correct_Diff_covid ~ poly(Political_LiberalConservative, 2), 
        data=filter(df, !is.na(Political_LiberalConservative)))

display(parameters(m))

estimate_relation(m, length=30) |> 
  ggplot(aes(x=Political_LiberalConservative, y=Predicted)) +
  # geom_jitter(data=filter(df, !is.na(Political_LiberalConservative)), 
  #             aes(y=MIST_correct_Pretest_covid), alpha=0.2, size=3) +
  geom_ribbon(aes(ymin=CI_low, ymax=CI_high), alpha=0.2) +
  geom_line() +
  labs(y="MIST COVID (% Correct difference Post-Pre)", x="Political Identification")
```

## MIST COVID (% Correct difference Post-Pre) (independent/predictor) & MIST COVID (% Correct Pretest)

```{r}
m <- lm(MIST_correct_Diff_covid ~ MIST_correct_Pretest_covid, 
        data=filter(df, !is.na(MIST_correct_Pretest_covid)))

display(parameters(m))

estimate_relation(m, length=30) |> 
  ggplot(aes(x=MIST_correct_Pretest_covid, y=Predicted)) +
  # geom_jitter(data=filter(df, !is.na(Political_LiberalConservative)), 
  #             aes(y=MIST_correct_Pretest_covid), alpha=0.2, size=3) +
  geom_ribbon(aes(ymin=CI_low, ymax=CI_high), alpha=0.2) +
  geom_line() +
  labs(x="MIST COVID (% Correct pre-test)", y="MIST COVID (% Correct difference Post-Pre)")
```

## MIST General (% Correct difference Post-Pre) (independent/predictor) & MIST General (% Correct Pretest)

```{r}
m <- lm(MIST_correct_Diff_general ~ MIST_correct_Pretest_general, 
        data=filter(df, !is.na(MIST_correct_Pretest_general)))

display(parameters(m))

estimate_relation(m, length=30) |> 
  ggplot(aes(x=MIST_correct_Pretest_general, y=Predicted)) +
  # geom_jitter(data=filter(df, !is.na(Political_LiberalConservative)), 
  #             aes(y=MIST_correct_Pretest_covid), alpha=0.2, size=3) +
  geom_ribbon(aes(ymin=CI_low, ymax=CI_high), alpha=0.2) +
  geom_line() +
  labs(x="MIST General (% Correct pre-test)", y="MIST General (% Correct difference Post-Pre)")
```


## self-identified political ideology (independent/predictor) & MIST COVID (% Correct difference Post-Pre) (dependent/outcome)

```{r}
m <- lm(MIST_correct_Diff_covid ~ poly(Political_LiberalConservative, 2), 
        data=filter(df, !is.na(Political_LiberalConservative)))

display(parameters(m))

estimate_relation(m, length=30) |> 
  ggplot(aes(x=Political_LiberalConservative, y=Predicted)) +
  # geom_jitter(data=filter(df, !is.na(Political_LiberalConservative)), 
  #             aes(y=MIST_correct_Pretest_covid), alpha=0.2, size=3) +
  geom_ribbon(aes(ymin=CI_low, ymax=CI_high), alpha=0.2) +
  geom_line() +
  labs(y="MIST COVID (% Correct difference Post-Pre)", x="Political Identification")
```

## Gender (independent/predictor) & MIST COVID (% Correct difference post-pre) (dependent/outcome)

```{r}
# Categorical
df$Gender <- as.factor(df$Gender)
m <- lm(MIST_correct_Diff_covid ~ Gender, 
        data=filter(df, Gender != "Non-Binary" & Gender != "Prefer not to answer"))


display(estimate_contrasts(m, contrast="Gender", p_adjust="none"))

estimate_means(m, by = c("Gender")) |> 
  ggplot(aes(x=Gender, y=Mean)) +
  geom_line(aes(group=1)) + 
  geom_pointrange(aes(ymin=CI_low, ymax=CI_high)) +
  labs(y="MIST-Covid (% Correct difference post-pre)", x="Gender")
```

## Gender (independent/predictor) & MIST COVID (% Correct pretest) (dependent/outcome)

```{r}
# Categorical
df$Gender <- as.factor(df$Gender)
m <- lm(MIST_correct_Pretest_covid ~ Gender, 
        data=filter(df, Gender != "Non-Binary" & Gender != "Prefer not to answer"))


display(estimate_contrasts(m, contrast="Gender", p_adjust="none"))

estimate_means(m, by = c("Gender")) |> 
  ggplot(aes(x=Gender, y=Mean)) +
  geom_line(aes(group=1)) + 
  geom_pointrange(aes(ymin=CI_low, ymax=CI_high)) +
  labs(y="MIST-Covid (% Correct Pre-test)", x="Gender")
```

## Education (independent/predictor) & MIST COVID (% Correct difference post-pre) (dependent/outcome)

##this one is not working right at the moment, bachelor refuses to show up for me for some reason now

```{r}
# Categorical
df$Education <- as.factor(df$Education)
df <- df %>% filter(!is.na(Education))
unique(trimws(df$Education))

m <- lm(MIST_correct_Diff_covid ~ Education, 
        data=filter(df, Education != "Other"))

display(estimate_contrasts(m, contrast="Education", p_adjust="none"))

estimate_means(m, by = c("Education")) |> 
  ggplot(aes(x=Education, y=Mean)) +
  geom_line(aes(group=1)) + 
  geom_pointrange(aes(ymin=CI_low, ymax=CI_high)) +
  labs(y="MIST-Covid (% Correct difference post-pre)", x="Education")
```

## Education (independent/predictor) & MIST COVID (% Correct pretest) (dependent/outcome)

##this one is not working right at the moment, bachelor refuses to show up for me for some reason now


```{r}
# Categorical
df$Education <- as.factor(df$Education)
m <- lm(MIST_correct_Pretest_covid ~ Education, 
        data=filter(df, Education != "Other"))

display(estimate_contrasts(m, contrast="Education", p_adjust="none"))

estimate_means(m, by = c("Education")) |> 
  ggplot(aes(x=Education, y=Mean)) +
  geom_line(aes(group=1)) + 
  geom_pointrange(aes(ymin=CI_low, ymax=CI_high)) +
  labs(y="MIST-Covid (% Correct Pre-test)", x="Education")
```

## Age (independent/predictor) & MIST COVID (% Correct pretest) (dependent/outcome)

```{r}
m <- lm(MIST_correct_Pretest_covid ~ Age, 
        data=df)

display(parameters(m))

estimate_relation(m, length=30) |> 
  ggplot(aes(x=Age, y=Predicted)) +
  # geom_jitter(data=filter(df, !is.na(Political_LiberalConservative)), 
  #             aes(y=MIST_correct_Pretest_covid), alpha=0.2, size=3) +
  geom_ribbon(aes(ymin=CI_low, ymax=CI_high), alpha=0.2) +
  geom_line() +
  labs(y="MIST-Covid (% Correct Pretest)", x="Age")
```

## Age (independent/predictor) & MIST COVID (% Correct difference post-pre) (dependent/outcome)

## why does this one show essentially no change in intervention effect size whatsoever? Feels like I made a mistake here somewhere

```{r}
m <- lm(MIST_correct_Diff_covid ~ Age, 
        data=df)

display(parameters(m))

estimate_relation(m, length=30) |> 
  ggplot(aes(x=Age, y=Predicted)) +
  # geom_jitter(data=filter(df, !is.na(Political_LiberalConservative)), 
  #             aes(y=MIST_correct_Pretest_covid), alpha=0.2, size=3) +
  geom_ribbon(aes(ymin=CI_low, ymax=CI_high), alpha=0.2) +
  geom_line() +
  labs(y="MIST-Covid (% Correct difference post-pre)", x="Age")
```

## Intervention vs Control (independent/predictor) & MIST COVID (% Correct difference post-pre) (dependent/outcome)

```{r}
# Categorical
m <- lm(MIST_correct_Diff_covid ~ Intervention, 
        data=df)

display(estimate_contrasts(m, contrast="Intervention", p_adjust="none"))

estimate_means(m, by = "Intervention") |> 
  ggplot(aes(x=Intervention, y=Mean)) +
  geom_line(aes(group=1)) + 
  geom_pointrange(aes(ymin=CI_low, ymax=CI_high)) +
  labs(y="MIST-Covid (% Correct difference post-pre)", x="Intervention vs Control")
```

