---
title: "FaceNewsIntervention - Data Analysis"
editor: source
editor_options: 
  chunk_output_type: console
format:
  html:
    output-file: "analysis_intervention_report.html"
    code-fold: true
    self-contained: true
    toc: true
---

## Data Preparation

```{r}
#| message: false
#| warning: false

library(emmeans)
library(tidyverse)
library(easystats)
library(patchwork)
library(ggside)
```

```{r}
#| code-fold: false

df <- read.csv("../data/data.csv")
dfmist <- read.csv("../data/data_mist.csv")

```

::: panel-tabset

# Examples

## Example for Continuous Variable

```{r}

m <- lm(MIST_correct_Pretest_covid ~ poly(Political_LiberalConservative, 2), 
        data=filter(df, !is.na(Political_LiberalConservative)))

display(parameters(m))

estimate_relation(m, length=30) |> 
  ggplot(aes(x=Political_LiberalConservative, y=Predicted)) +
  # geom_jitter(data=filter(df, !is.na(Political_LiberalConservative)), 
  #             aes(y=MIST_correct_Pretest_covid), alpha=0.2, size=3) +
  geom_ribbon(aes(ymin=CI_low, ymax=CI_high), alpha=0.2) +
  geom_line() +
  labs(y="MIST-Covid (% Correct Pretest)", x="Political Identification")
```

## Example for Categorical Variable

```{r}
# Categorical
m <- lm(MIST_correct_Pretest_covid ~ Political_Affiliation, 
        data=filter(df, Political_Affiliation != "None or Independent"))

display(estimate_contrasts(m, contrast="Political_Affiliation", p_adjust="none"))

estimate_means(m, by = c("Political_Affiliation")) |> 
  ggplot(aes(x=Political_Affiliation, y=Mean)) +
  geom_line(aes(group=1)) + 
  geom_pointrange(aes(ymin=CI_low, ymax=CI_high)) +
  labs(y="MIST-Covid (% Correct Pretest)", x="Political Affiliation")
```

------------------------------------------------------------------------

## Example for Multivariate Model

```{r}
# model <- glmmTMB::glmmTMB(Correct ~ Intervention * Condition * Topic + (1|Participant) + (1|QuestionID), 
#                           data=dfmist, family=binomial())
# 
# model_means <- modelbased::estimate_means(model, by=c("Intervention", "Condition", "Topic"))
# 
# model_means |> 
#   mutate(Condition = fct_rev(Condition)) |> 
#   ggplot(aes(x=Condition, y=Probability, color=Intervention)) +
#   geom_line(aes(group=Intervention), position=position_dodge(width=0.1)) +
#   geom_pointrange(aes(ymin=CI_low, ymax=CI_high), position=position_dodge(width=0.1)) +
#   facet_wrap(~Topic)
```

------------------------------------------------------------------------

# MIST difference vs pre-test

## MIST (% Correct difference Post-Pre) (independent/predictor) & MIST (% Correct Pretest)

```{r}
df <- df %>%
  mutate(MIST_correct_Pretest_avg = (MIST_correct_Pretest_covid + MIST_correct_Pretest_general) / 2)


m <- lm(MIST_correct_Diff ~ Intervention * MIST_correct_Pretest_covid + Intervention * MIST_correct_Pretest_general, 
        data = filter(df, !is.na(MIST_correct_Pretest_covid) & !is.na(MIST_correct_Pretest_general)))


display(parameters(m))

estimate_relation(m, length=30) |> 
  ggplot(aes(x=MIST_correct_Pretest_covid, y=Predicted)) +
  # geom_jitter(data=filter(df, !is.na(Political_LiberalConservative)), 
  #             aes(y=MIST_correct_Pretest_covid), alpha=0.2, size=3) +
  geom_ribbon(aes(ymin=CI_low, ymax=CI_high, fill=Intervention), alpha=0.2) +
  geom_line(aes(color=Intervention)) +
  labs(x="MIST (% Correct pre-test)", y="MIST (% Correct difference Post-Pre)")

```


## MIST COVID (% Correct difference Post-Pre) (independent/predictor) & MIST COVID (% Correct Pretest)

```{r}
m <- lm(MIST_correct_Diff_covid ~ Intervention/MIST_correct_Pretest_covid, 
        data=filter(df, !is.na(MIST_correct_Pretest_covid)))

display(parameters(m))

estimate_relation(m, length=30) |> 
  ggplot(aes(x=MIST_correct_Pretest_covid, y=Predicted)) +
  # geom_jitter(data=filter(df, !is.na(Political_LiberalConservative)), 
  #             aes(y=MIST_correct_Pretest_covid), alpha=0.2, size=3) +
  geom_ribbon(aes(ymin=CI_low, ymax=CI_high, fill=Intervention), alpha=0.2) +
  geom_line(aes(color=Intervention)) +
  labs(x="MIST COVID (% Correct pre-test)", y="MIST COVID (% Correct difference Post-Pre)")
```

## MIST General (% Correct difference Post-Pre) (independent/predictor) & MIST General (% Correct Pretest)

```{r}
m <- lm(MIST_correct_Diff_general ~ Intervention/MIST_correct_Pretest_general, 
        data=filter(df, !is.na(MIST_correct_Pretest_general)))

display(parameters(m))

estimate_relation(m, length=30) |> 
  ggplot(aes(x=MIST_correct_Pretest_general, y=Predicted)) +
  # geom_jitter(data=filter(df, !is.na(Political_LiberalConservative)), 
  #             aes(y=MIST_correct_Pretest_covid), alpha=0.2, size=3) +
  geom_ribbon(aes(ymin=CI_low, ymax=CI_high, fill=Intervention), alpha=0.2) +
  geom_line(aes(colour=Intervention)) +
  labs(x="MIST General (% Correct pre-test)", y="MIST General (% Correct difference Post-Pre)")
```



# Gender

## Gender (independent/predictor) & MIST (% Correct difference post-pre) (dependent/outcome)

```{r}
# Categorical
df$Gender <- as.factor(df$Gender)
m <- lm(MIST_correct_Diff ~ Gender, 
        data=filter(df, Gender != "Non-Binary" & Gender != "Prefer not to answer"))


display(estimate_contrasts(m, contrast="Gender", p_adjust="none"))

estimate_means(m, by = c("Gender")) |> 
  ggplot(aes(x=Gender, y=Mean)) +
  geom_line(aes(group=1)) + 
  geom_pointrange(aes(ymin=CI_low, ymax=CI_high)) +
  labs(y="MIST (% Correct difference post-pre)", x="Gender")
```

## Gender (independent/predictor) & MIST (% Correct pretest) (dependent/outcome)

```{r}
# Categorical
df$Gender <- as.factor(df$Gender)
m <- lm(MIST_correct_Pretest_avg ~ Gender, 
        data=filter(df, Gender != "Non-Binary" & Gender != "Prefer not to answer"))


display(estimate_contrasts(m, contrast="Gender", p_adjust="none"))

estimate_means(m, by = c("Gender")) |> 
  ggplot(aes(x=Gender, y=Mean)) +
  geom_line(aes(group=1)) + 
  geom_pointrange(aes(ymin=CI_low, ymax=CI_high)) +
  labs(y="MIST (% Correct Pre-test)", x="Gender")
```

# Education

## Education (independent/predictor) & MIST (% Correct difference post-pre) (dependent/outcome)

```{r}
# Categorical
df$Education <- as.factor(df$Education)
df <- df %>% filter(!is.na(Education))
unique(trimws(df$Education))

m <- lm(MIST_correct_Diff ~ Education, 
        data=filter(df, Education != "Other"))

display(estimate_contrasts(m, contrast="Education", p_adjust="none"))

estimate_means(m, by = c("Education")) |> 
  ggplot(aes(x=Education, y=Mean)) +
  geom_line(aes(group=1)) + 
  geom_pointrange(aes(ymin=CI_low, ymax=CI_high)) +
  labs(y="MIST (% Correct difference post-pre)", x="Education")
```

## Education (independent/predictor) & MIST (% Correct pretest) (dependent/outcome)

```{r}
# Categorical
df$Education <- as.factor(df$Education)
m <- lm(MIST_correct_Pretest_avg ~ Education, 
        data=filter(df, Education != "Other"))

display(estimate_contrasts(m, contrast="Education", p_adjust="none"))

estimate_means(m, by = c("Education")) |> 
  ggplot(aes(x=Education, y=Mean)) +
  geom_line(aes(group=1)) + 
  geom_pointrange(aes(ymin=CI_low, ymax=CI_high)) +
  labs(y="MIST (% Correct Pre-test)", x="Education")
```

# Age

## Age (independent/predictor) & MIST (% Correct pretest) (dependent/outcome)

```{r}
m <- lm(MIST_correct_Pretest_avg ~ Age, 
        data=df)

display(parameters(m))

estimate_relation(m, length=30) |> 
  ggplot(aes(x=Age, y=Predicted)) +
  # geom_jitter(data=filter(df, !is.na(Political_LiberalConservative)), 
  #             aes(y=MIST_correct_Pretest_covid), alpha=0.2, size=3) +
  geom_ribbon(aes(ymin=CI_low, ymax=CI_high), alpha=0.2) +
  geom_line() +
  labs(y="MIST (% Correct Pretest)", x="Age")
```

## Age (independent/predictor) & MIST (% Correct difference post-pre) (dependent/outcome)

## why does this one show essentially no change in intervention effect size whatsoever? Feels like I made a mistake here somewhere

```{r}
m <- lm(MIST_correct_Diff ~ Age, 
        data=df)

display(parameters(m))

estimate_relation(m, length=30) |> 
  ggplot(aes(x=Age, y=Predicted)) +
  # geom_jitter(data=filter(df, !is.na(Political_LiberalConservative)), 
  #             aes(y=MIST_correct_Pretest_covid), alpha=0.2, size=3) +
  geom_ribbon(aes(ymin=CI_low, ymax=CI_high), alpha=0.2) +
  geom_line() +
  labs(y="MIST (% Correct difference post-pre)", x="Age")
```

# Intervention vs Control

## Intervention vs Control (independent/predictor) & MOCRI (% Correct difference post-pre) (dependent/outcome)

```{r}
# Categorical
m <- lm(MOCRI_correct_Diff ~ Intervention, 
        data=df)

display(estimate_contrasts(m, contrast="Intervention", p_adjust="none"))

estimate_means(m, by = "Intervention") |> 
  ggplot(aes(x=Intervention, y=Mean)) +
  geom_line(aes(group=1)) + 
  geom_pointrange(aes(ymin=CI_low, ymax=CI_high)) +
  labs(y="MOCRI (% Correct difference post-pre)", x="Intervention vs Control")
```

## Intervention vs Control (independent/predictor) & MOCRI (% dprime difference post-pre) (dependent/outcome)

```{r}
# Categorical
m <- lm(MOCRI_dprime_Diff ~ Intervention, 
        data=df)

display(estimate_contrasts(m, contrast="Intervention", p_adjust="none"))

estimate_means(m, by = "Intervention") |> 
  ggplot(aes(x=Intervention, y=Mean)) +
  geom_line(aes(group=1)) + 
  geom_pointrange(aes(ymin=CI_low, ymax=CI_high)) +
  labs(y="MOCRI (% dprime difference post-pre)", x="Intervention vs Control")
```

## Intervention vs Control (independent/predictor) & MIST COVID (% Correct difference post-pre) (dependent/outcome)

```{r}
# Categorical
m <- lm(MIST_correct_Diff_covid ~ Intervention, 
        data=df)

display(estimate_contrasts(m, contrast="Intervention", p_adjust="none"))

estimate_means(m, by = "Intervention") |> 
  ggplot(aes(x=Intervention, y=Mean)) +
  geom_line(aes(group=1)) + 
  geom_pointrange(aes(ymin=CI_low, ymax=CI_high)) +
  labs(y="MIST-Covid (% Correct difference post-pre)", x="Intervention vs Control")
```

## Intervention vs Control (independent/predictor) & MIST COVID (dprime difference post-pre) (dependent/outcome)

```{r}
# Categorical
m <- lm(MIST_dprime_Diff_covid ~ Intervention, 
        data=df)

display(estimate_contrasts(m, contrast="Intervention", p_adjust="none"))

estimate_means(m, by = "Intervention") |> 
  ggplot(aes(x=Intervention, y=Mean)) +
  geom_line(aes(group=1)) + 
  geom_pointrange(aes(ymin=CI_low, ymax=CI_high)) +
  labs(y="MIST-Covid (dprime difference post-pre)", x="Intervention vs Control")
```

## Intervention vs Control (independent/predictor) & MIST general (% Correct difference post-pre) (dependent/outcome)

```{r}
# Categorical
m <- lm(MIST_correct_Diff_general ~ Intervention, 
        data=df)

display(estimate_contrasts(m, contrast="Intervention", p_adjust="none"))

estimate_means(m, by = "Intervention") |> 
  ggplot(aes(x=Intervention, y=Mean)) +
  geom_line(aes(group=1)) + 
  geom_pointrange(aes(ymin=CI_low, ymax=CI_high)) +
  labs(y="MIST-general (% Correct difference post-pre)", x="Intervention vs Control")
```

## Intervention vs Control (independent/predictor) & MIST general (dprime difference post-pre) (dependent/outcome)

```{r}
# Categorical
m <- lm(MIST_dprime_Diff_general ~ Intervention, 
        data=df)

display(estimate_contrasts(m, contrast="Intervention", p_adjust="none"))

estimate_means(m, by = "Intervention") |> 
  ggplot(aes(x=Intervention, y=Mean)) +
  geom_line(aes(group=1)) + 
  geom_pointrange(aes(ymin=CI_low, ymax=CI_high)) +
  labs(y="MIST-general (dprime difference post-pre)", x="Intervention vs Control")
```

## Intervention vs Control (independent/predictor) & MIST total (% Correct difference post-pre) (dependent/outcome)

```{r}
# Categorical
m <- lm(MIST_correct_Diff ~ Intervention, 
        data=df)

display(estimate_contrasts(m, contrast="Intervention", p_adjust="none"))

estimate_means(m, by = "Intervention") |> 
  ggplot(aes(x=Intervention, y=Mean)) +
  geom_line(aes(group=1)) + 
  geom_pointrange(aes(ymin=CI_low, ymax=CI_high)) +
  labs(y="MIST-TOTAL (% Correct difference post-pre)", x="Intervention vs Control")
```

## Intervention vs Control (independent/predictor) & MIST total (dprime difference post-pre) (dependent/outcome)

```{r}
# Categorical
m <- lm(MIST_dprime_Diff ~ Intervention, 
        data=df)

display(estimate_contrasts(m, contrast="Intervention", p_adjust="none"))

estimate_means(m, by = "Intervention") |> 
  ggplot(aes(x=Intervention, y=Mean)) +
  geom_line(aes(group=1)) + 
  geom_pointrange(aes(ymin=CI_low, ymax=CI_high)) +
  labs(y="MIST-TOTAL (dprime difference post-pre)", x="Intervention vs Control")
```

# Confidence

## CONFIDENCE \[political ideology\]

```{r}
df_long <- df |> 
  pivot_longer(cols = starts_with("MIST_Confidence_"), 
               names_to = "Category", values_to = "Confidence") |> 
  mutate(TestPhase = ifelse(grepl("Pretest", Category), "Pretest", "Posttest"))

# Filter pretest data
df_pre <- filter(df_long, TestPhase == "Pretest")

# Run model
m_pre <- lm(Confidence ~ poly(Political_LiberalConservative, 2) * Category, 
            data = filter(df_pre, !is.na(Political_LiberalConservative)))

# Print model summary (this will show the p-values)
summary(m_pre)

# Print the summary of the pretest model, including overall significance
summary(m_pre)

# Print the p-value for the F-statistic (overall model)
summary(m_pre)$fstatistic


# Predict values
preds_pre <- estimate_relation(m_pre, length=30)

# Plot
ggplot(preds_pre, aes(x=Political_LiberalConservative, y=Predicted, color=Category)) +
  geom_ribbon(aes(ymin=CI_low, ymax=CI_high, fill=Category), alpha=0.1) +
  geom_line(size=1) +
  labs(y="Confidence", x="Political Identification", title="Pretest Confidence") +
  theme_minimal()


##___________________________________________________________

# Filter posttest data
df_post <- filter(df_long, TestPhase == "Posttest")

# Run model
m_post <- lm(Confidence ~ poly(Political_LiberalConservative, 2) * Category, 
             data = filter(df_post, !is.na(Political_LiberalConservative)))

# Print model summary (this will show the p-values)
summary(m_post)

# Predict values
preds_post <- estimate_relation(m_post, length=30)

# Plot
ggplot(preds_post, aes(x=Political_LiberalConservative, y=Predicted, color=Category)) +
  geom_ribbon(aes(ymin=CI_low, ymax=CI_high, fill=Category), alpha=0.1) +
  geom_line(size=1) +
  labs(y="Confidence", x="Political Identification", title="Posttest Confidence") +
  theme_minimal()


```

## CONFIDENCE \[intervention vs control\] pretest and posttest

```{r}
df_long <- df |> 
  pivot_longer(cols = starts_with("MIST_Confidence_"), 
               names_to = "Category", values_to = "Confidence") |> 
  mutate(TestPhase = ifelse(grepl("Pretest", Category), "Pretest", "Posttest"))

# Filter pretest data
df_pre <- filter(df_long, TestPhase == "Pretest")

# Run model for pretest, using 'Intervention' instead of political ideology
m_pre <- lm(Confidence ~ Intervention * Category, 
            data = filter(df_pre, !is.na(Intervention)))

# Print model summary for pretest
summary(m_pre)

# Predict values for pretest
preds_pre <- estimate_relation(m_pre, length=30)

# Plot for pretest
ggplot(preds_pre, aes(x=Intervention, y=Predicted, fill=Category)) +
  geom_boxplot() +
  labs(y="Confidence", x="Intervention Group", title="Pretest Confidence by Intervention Group") +
  theme_minimal()

##___________________________________________________________

# Filter posttest data
df_post <- filter(df_long, TestPhase == "Posttest")

# Run model for posttest, using 'Intervention' instead of political ideology
m_post <- lm(Confidence ~ Intervention * Category, 
             data = filter(df_post, !is.na(Intervention)))

# Print model summary for posttest
summary(m_post)

# Predict values for posttest
preds_post <- estimate_relation(m_post, length=30)

# Plot for posttest
ggplot(preds_post, aes(x=Intervention, y=Predicted, fill=Category)) +
  geom_boxplot() +
  labs(y="Confidence", x="Intervention Group", title="Posttest Confidence by Intervention Group") +
  theme_minimal()

```

## CONFIDENCE \[intervention group only\] confidence and time

```{r}
# Linear model for MIST Confidence difference based on Intervention, Pretest to Posttest
m_intervention <- lm(MIST_Confidence_Posttest - MIST_Confidence_Pretest ~ Intervention, 
                     data = df)

# Estimate contrasts (for significance testing between intervention and control)
display(estimate_contrasts(m_intervention, contrast="Intervention", p_adjust="none"))

# Estimate means by intervention group
estimate_means(m_intervention, by = "Intervention") |> 
  ggplot(aes(x = Intervention, y = Mean)) +
  geom_line(aes(group = 1)) + 
  geom_pointrange(aes(ymin = CI_low, ymax = CI_high)) +
  labs(y = "MIST Confidence Difference (Posttest - Pretest)", x = "Intervention vs Control")

```

## confidence posttest intervention vs control

```{r}
# Categorical
m <- lm((MIST_Confidence_Posttest) ~ Intervention, 
        data=df)

display(estimate_contrasts(m, contrast="Intervention", p_adjust="none"))

estimate_means(m, by = "Intervention") |> 
  ggplot(aes(x=Intervention, y=Mean)) +
  geom_line(aes(group=1)) + 
  geom_pointrange(aes(ymin=CI_low, ymax=CI_high)) +
  labs(y="Confidence (posttest ONLY)", x="Intervention vs Control")
```

## t-test intervention group ONLY, pretest vs posttest confidence

```{r}
# Subset the data for just the BadNews intervention group
df_badnews <- filter(df, Intervention == "BadNews")

# Paired t-test comparing pretest and posttest confidence
t.test(df_badnews$MIST_Confidence_Pretest, 
       df_badnews$MIST_Confidence_Posttest, 
       paired = TRUE)

```

# Criterion

## CRITERION overall difference post-pre intervention vs control

```{r}
# Create a new column for the overall criterion post-pre difference (averaging covid and general)
df$Criterion_Difference <- (df$MIST_criterion_Diff_covid + df$MIST_criterion_Diff_general) / 2

# Linear Model for Criterion Difference (Post - Pre) by Intervention
m_criterion_diff <- lm(Criterion_Difference ~ Intervention, data = df)

# Displaying the estimated contrasts for the 'Intervention' variable
display(estimate_contrasts(m_criterion_diff, contrast = "Intervention", p_adjust = "none"))

# Estimate means by 'Intervention' group
estimate_means(m_criterion_diff, by = "Intervention") |> 
  ggplot(aes(x = Intervention, y = Mean)) +
  geom_line(aes(group = 1)) + 
  geom_pointrange(aes(ymin = CI_low, ymax = CI_high)) +
  labs(y = "Criterion Difference (Post - Pre)", x = "Intervention vs Control") + 
  ggtitle("Effect of Intervention on Overall Criterion Difference (Post - Pre)")

```

## CRITERION MIST-COVID difference post-pre intervention vs control

```{r}

# Linear Model for Criterion Difference (Post - Pre) by Intervention
m <- lm(MIST_criterion_Diff_covid ~ Intervention, data = df)

# Displaying the estimated contrasts for the 'Intervention' variable
display(estimate_contrasts(m, contrast = "Intervention", p_adjust = "none"))

# Estimate means by 'Intervention' group
estimate_means(m, by = "Intervention") |> 
  ggplot(aes(x = Intervention, y = Mean)) +
  geom_line(aes(group = 1)) + 
  geom_pointrange(aes(ymin = CI_low, ymax = CI_high)) +
  labs(y = "Criterion Difference (Post - Pre)", x = "Intervention vs Control") + 
  ggtitle("Effect of Intervention on MIST-COVID Criterion Difference (Post - Pre)")

```

## CRITERION MIST-GENERAL difference post-pre intervention vs control

## this appears to show opposing results in the visual graph and printed modelling results. I interpret the results as saying the badnews group performed worse, but the graph seems to show them performing better. not sure what's up here. I did a series of verifications but never found an error

```{r}

# Linear Model for Criterion Difference (Post - Pre) by Intervention
m <- lm(MIST_criterion_Diff_general ~ Intervention, data = df)

# Displaying the estimated contrasts for the 'Intervention' variable
display(estimate_contrasts(m, contrast = "Intervention", p_adjust = "none"))

# Estimate means by 'Intervention' group
estimate_means(m, by = "Intervention") |> 
  ggplot(aes(x = Intervention, y = Mean)) +
  geom_line(aes(group = 1)) + 
  geom_pointrange(aes(ymin = CI_low, ymax = CI_high)) +
  labs(y = "Criterion Difference (Post - Pre)", x = "Intervention vs Control") + 
  ggtitle("Effect of Intervention on MIST-general Criterion Difference (Post - Pre)")

```

## Criterion and political ideology

##I'm not sure how to interpret this, think there may be errors somewhere involved? Also, at the moment contagion measures ignore fake vs real questions, which I think may just be an oversight but i'm not sure how to correct it in the cleaning script

```{r}
df_long <- df |> 
  pivot_longer(cols = starts_with("MIST_criterion_"), 
               names_to = "Category", values_to = "Criterion") |> 
  mutate(TestPhase = ifelse(grepl("Pretest", Category), "Pretest", "Posttest"))

# Filter pretest data
df_pre <- filter(df_long, TestPhase == "Pretest")

# Run model for pretest criterion
m_pre <- lm(Criterion ~ poly(Political_LiberalConservative, 2) * Category, 
            data = filter(df_pre, !is.na(Political_LiberalConservative)))

# Print model summary (this will show the p-values)
summary(m_pre)

# Print the summary of the pretest model, including overall significance
summary(m_pre)

# Print the p-value for the F-statistic (overall model)
summary(m_pre)$fstatistic

# Predict values
preds_pre <- estimate_relation(m_pre, length=30)

# Plot
ggplot(preds_pre, aes(x=Political_LiberalConservative, y=Predicted, color=Category)) +
  geom_ribbon(aes(ymin=CI_low, ymax=CI_high, fill=Category), alpha=0.1) +
  geom_line(size=1) +
  labs(y="Criterion", x="Political Identification", title="Pretest Criterion") +
  theme_minimal()


##___________________________________________________________

# Filter posttest data
df_post <- filter(df_long, TestPhase == "Posttest")

# Run model for posttest criterion
m_post <- lm(Criterion ~ poly(Political_LiberalConservative, 2) * Category, 
             data = filter(df_post, !is.na(Political_LiberalConservative)))

# Print model summary (this will show the p-values)
summary(m_post)

# Predict values
preds_post <- estimate_relation(m_post, length=30)

# Plot
ggplot(preds_post, aes(x=Political_LiberalConservative, y=Predicted, color=Category)) +
  geom_ribbon(aes(ymin=CI_low, ymax=CI_high, fill=Category), alpha=0.1) +
  geom_line(size=1) +
  labs(y="Criterion", x="Political Identification", title="Posttest Criterion") +
  theme_minimal()

```
# Multivariate Model
```{r}

model <- glmmTMB::glmmTMB(Correct ~ QuestionType / Topic  / (Condition * Intervention) + (1|Participant), data=dfmist, family="binomial")

estimate_relation(model) |> 
  ggplot(aes(x=Condition, y=Predicted)) +
  geom_line(aes(color=Intervention, group=Intervention)) + 
  geom_pointrange(aes(color=Intervention, ymin=CI_low, ymax=CI_high)) +
  facet_wrap(~QuestionType * Topic, scales="free")


estimate_contrasts(model, contrast=c("Condition"), by=c("Topic","Intervention"))

```
:::

```{r}
#browseURL("analysis_report.html")  # Use this in the analysis file

```
