---
title: "analysis_covariates"
editor: source
editor_options: 
  chunk_output_type: console
format:
  html:
    code-fold: true
    self-contained: true
    toc: true
---


## Data Preparation

```{r}
#| message: false
#| warning: false

library(emmeans)
library(tidyverse)
library(easystats)
library(patchwork)
library(ggside)
```

```{r}
#| code-fold: false

df <- read.csv("../data/data.csv")
dfmist <- read.csv("../data/data_mist.csv")
dfmocri <- read.csv("../data/data_mocri.csv")

```

::: panel-tabset

# Examples

## Example for Continuous Variable

```{r}

m <- lm(MIST_correct_Pretest_covid ~ poly(Political_LiberalConservative, 2), 
        data=filter(df, !is.na(Political_LiberalConservative)))

display(parameters(m))

estimate_relation(m, length=30) |> 
  ggplot(aes(x=Political_LiberalConservative, y=Predicted)) +
  # geom_jitter(data=filter(df, !is.na(Political_LiberalConservative)), 
  #             aes(y=MIST_correct_Pretest_covid), alpha=0.2, size=3) +
  geom_ribbon(aes(ymin=CI_low, ymax=CI_high), alpha=0.2) +
  geom_line() +
  labs(y="MIST-Covid (% Correct Pretest)", x="Political Identification")
```

## Example for Categorical Variable

```{r}
# Categorical
m <- lm(MIST_correct_Pretest_covid ~ Political_Affiliation, 
        data=filter(df, Political_Affiliation != "None or Independent"))

display(estimate_contrasts(m, contrast="Political_Affiliation", p_adjust="none"))

estimate_means(m, by = c("Political_Affiliation")) |> 
  ggplot(aes(x=Political_Affiliation, y=Mean)) +
  geom_line(aes(group=1)) + 
  geom_pointrange(aes(ymin=CI_low, ymax=CI_high)) +
  labs(y="MIST-Covid (% Correct Pretest)", x="Political Affiliation")
```

# Political ideology & questionnaires

## self-identified political ideology (independent/predictor) & VSA general score (dependent/outcome)

```{r}
m <- lm(VSA_General ~ poly(Political_LiberalConservative, 2), 
        data=filter(df, !is.na(Political_LiberalConservative)))

display(parameters(m))

estimate_relation(m, length=30) |> 
  ggplot(aes(x=Political_LiberalConservative, y=Predicted)) +
  # geom_jitter(data=filter(df, !is.na(Political_LiberalConservative)), 
  #             aes(y=MIST_correct_Pretest_covid), alpha=0.2, size=3) +
  geom_ribbon(aes(ymin=CI_low, ymax=CI_high), alpha=0.2) +
  geom_line() +
  labs(y="VSA General Mean Score", x="Political Identification")
```

## self-identified political ideology (independent/predictor) & VSA authoritarianism score (dependent/outcome)

```{r}
m <- lm(VSA_Authoritarianism ~ poly(Political_LiberalConservative, 2), 
        data=filter(df, !is.na(Political_LiberalConservative)))

display(parameters(m))

estimate_relation(m, length=30) |> 
  ggplot(aes(x=Political_LiberalConservative, y=Predicted)) +
  # geom_jitter(data=filter(df, !is.na(Political_LiberalConservative)), 
  #             aes(y=MIST_correct_Pretest_covid), alpha=0.2, size=3) +
  geom_ribbon(aes(ymin=CI_low, ymax=CI_high), alpha=0.2) +
  geom_line() +
  labs(y="VSA Authoritarianism Score", x="Political Identification")
```


## self-identified political ideology (independent/predictor) & BFI_Agreeableness (dependent/outcome)

```{r}
m <- lm(BFI_Agreeableness ~ poly(Political_LiberalConservative, 2), 
        data=filter(df, !is.na(Political_LiberalConservative)))

display(parameters(m))

estimate_relation(m, length=30) |> 
  ggplot(aes(x=Political_LiberalConservative, y=Predicted)) +
  # geom_jitter(data=filter(df, !is.na(Political_LiberalConservative)), 
  #             aes(y=MIST_correct_Pretest_covid), alpha=0.2, size=3) +
  geom_ribbon(aes(ymin=CI_low, ymax=CI_high), alpha=0.2) +
  geom_line() +
  labs(y="BFI Agreeableness", x="Political Identification")
```

## self-identified political ideology (independent/predictor) & BFI_Extraversion (dependent/outcome)

```{r}
m <- lm(BFI_Extraversion ~ poly(Political_LiberalConservative, 2), 
        data=filter(df, !is.na(Political_LiberalConservative)))

display(parameters(m))

estimate_relation(m, length=30) |> 
  ggplot(aes(x=Political_LiberalConservative, y=Predicted)) +
  # geom_jitter(data=filter(df, !is.na(Political_LiberalConservative)), 
  #             aes(y=MIST_correct_Pretest_covid), alpha=0.2, size=3) +
  geom_ribbon(aes(ymin=CI_low, ymax=CI_high), alpha=0.2) +
  geom_line() +
  labs(y="BFI Extraversion", x="Political Identification")
```

## self-identified political ideology (independent/predictor) & BFI_Conscientiousness (dependent/outcome)

```{r}
m <- lm(BFI_Conscientiousness ~ poly(Political_LiberalConservative, 2), 
        data=filter(df, !is.na(Political_LiberalConservative)))

display(parameters(m))

estimate_relation(m, length=30) |> 
  ggplot(aes(x=Political_LiberalConservative, y=Predicted)) +
  # geom_jitter(data=filter(df, !is.na(Political_LiberalConservative)), 
  #             aes(y=MIST_correct_Pretest_covid), alpha=0.2, size=3) +
  geom_ribbon(aes(ymin=CI_low, ymax=CI_high), alpha=0.2) +
  geom_line() +
  labs(y="BFI Conscientiousness", x="Political Identification")
```

## self-identified political ideology (independent/predictor) & BFI_Neuroticism (dependent/outcome)

```{r}
m <- lm(BFI_Neuroticism ~ poly(Political_LiberalConservative, 2), 
        data=filter(df, !is.na(Political_LiberalConservative)))

display(parameters(m))

estimate_relation(m, length=30) |> 
  ggplot(aes(x=Political_LiberalConservative, y=Predicted)) +
  # geom_jitter(data=filter(df, !is.na(Political_LiberalConservative)), 
  #             aes(y=MIST_correct_Pretest_covid), alpha=0.2, size=3) +
  geom_ribbon(aes(ymin=CI_low, ymax=CI_high), alpha=0.2) +
  geom_line() +
  labs(y="BFI_Neuroticism", x="Political Identification")
```

## self-identified political ideology (independent/predictor) & BFI_Openness (dependent/outcome)

```{r}
m <- lm(BFI_Openness ~ poly(Political_LiberalConservative, 2), 
        data=filter(df, !is.na(Political_LiberalConservative)))

display(parameters(m))

estimate_relation(m, length=30) |> 
  ggplot(aes(x=Political_LiberalConservative, y=Predicted)) +
  # geom_jitter(data=filter(df, !is.na(Political_LiberalConservative)), 
  #             aes(y=MIST_correct_Pretest_covid), alpha=0.2, size=3) +
  geom_ribbon(aes(ymin=CI_low, ymax=CI_high), alpha=0.2) +
  geom_line() +
  labs(y="BFI_Openness", x="Political Identification")
```

## self-identified political ideology (independent/predictor) & GCBS_General (dependent/outcome)

```{r}
m <- lm(GCBS_General ~ poly(Political_LiberalConservative, 2), 
        data=filter(df, !is.na(Political_LiberalConservative)))

display(parameters(m))

estimate_relation(m, length=30) |> 
  ggplot(aes(x=Political_LiberalConservative, y=Predicted)) +
  # geom_jitter(data=filter(df, !is.na(Political_LiberalConservative)), 
  #             aes(y=MIST_correct_Pretest_covid), alpha=0.2, size=3) +
  geom_ribbon(aes(ymin=CI_low, ymax=CI_high), alpha=0.2) +
  geom_line() +
  labs(y="GCBS_General", x="Political Identification")
```

## self-identified political ideology (independent/predictor) & GCBS_Control (dependent/outcome)

```{r}
m <- lm(GCBS_Control ~ poly(Political_LiberalConservative, 2), 
        data=filter(df, !is.na(Political_LiberalConservative)))

display(parameters(m))

estimate_relation(m, length=30) |> 
  ggplot(aes(x=Political_LiberalConservative, y=Predicted)) +
  # geom_jitter(data=filter(df, !is.na(Political_LiberalConservative)), 
  #             aes(y=MIST_correct_Pretest_covid), alpha=0.2, size=3) +
  geom_ribbon(aes(ymin=CI_low, ymax=CI_high), alpha=0.2) +
  geom_line() +
  labs(y="GCBS_Control", x="Political Identification")
```

## self-identified political ideology (independent/predictor) & GCBS_Wellbeing (dependent/outcome)

```{r}
m <- lm(GCBS_Wellbeing ~ poly(Political_LiberalConservative, 2), 
        data=filter(df, !is.na(Political_LiberalConservative)))

display(parameters(m))

estimate_relation(m, length=30) |> 
  ggplot(aes(x=Political_LiberalConservative, y=Predicted)) +
  # geom_jitter(data=filter(df, !is.na(Political_LiberalConservative)), 
  #             aes(y=MIST_correct_Pretest_covid), alpha=0.2, size=3) +
  geom_ribbon(aes(ymin=CI_low, ymax=CI_high), alpha=0.2) +
  geom_line() +
  labs(y="GCBS_Wellbeing", x="Political Identification")
```

## self-identified political ideology (independent/predictor) & GCBS_Malevolent (dependent/outcome)

```{r}
m <- lm(GCBS_Malevolent ~ poly(Political_LiberalConservative, 2), 
        data=filter(df, !is.na(Political_LiberalConservative)))

display(parameters(m))

estimate_relation(m, length=30) |> 
  ggplot(aes(x=Political_LiberalConservative, y=Predicted)) +
  # geom_jitter(data=filter(df, !is.na(Political_LiberalConservative)), 
  #             aes(y=MIST_correct_Pretest_covid), alpha=0.2, size=3) +
  geom_ribbon(aes(ymin=CI_low, ymax=CI_high), alpha=0.2) +
  geom_line() +
  labs(y="GCBS_Malevolent", x="Political Identification")
```

## self-identified political ideology (independent/predictor) & GCBS_Extraterrestrial (dependent/outcome)

```{r}
m <- lm(GCBS_Extraterrestrial ~ poly(Political_LiberalConservative, 2), 
        data=filter(df, !is.na(Political_LiberalConservative)))

display(parameters(m))

estimate_relation(m, length=30) |> 
  ggplot(aes(x=Political_LiberalConservative, y=Predicted)) +
  # geom_jitter(data=filter(df, !is.na(Political_LiberalConservative)), 
  #             aes(y=MIST_correct_Pretest_covid), alpha=0.2, size=3) +
  geom_ribbon(aes(ymin=CI_low, ymax=CI_high), alpha=0.2) +
  geom_line() +
  labs(y="GCBS_Extraterrestrial", x="Political Identification")
```

## self-identified political ideology (independent/predictor) & GCBS_GovernmentMalfeasance (dependent/outcome)

```{r}
m <- lm(GCBS_GovernmentMalfeasance ~ poly(Political_LiberalConservative, 2), 
        data=filter(df, !is.na(Political_LiberalConservative)))

display(parameters(m))

estimate_relation(m, length=30) |> 
  ggplot(aes(x=Political_LiberalConservative, y=Predicted)) +
  # geom_jitter(data=filter(df, !is.na(Political_LiberalConservative)), 
  #             aes(y=MIST_correct_Pretest_covid), alpha=0.2, size=3) +
  geom_ribbon(aes(ymin=CI_low, ymax=CI_high), alpha=0.2) +
  geom_line() +
  labs(y="GCBS_GovernmentMalfeasance", x="Political Identification")
```

# Political ideology & MIST

## self-identified political ideology (independent/predictor) & MIST COVID (% Correct Pre-test) (dependent/outcome)

```{r}
m <- lm(MIST_correct_Pretest_covid ~ Intervention/poly(Political_LiberalConservative, 2), 
        data=filter(df, !is.na(Political_LiberalConservative)))

display(parameters(m))

estimate_relation(m, length=30) |> 
  ggplot(aes(x=Political_LiberalConservative, y=Predicted)) +
  # geom_jitter(data=filter(df, !is.na(Political_LiberalConservative)), 
  #             aes(y=MIST_correct_Pretest_covid), alpha=0.2, size=3) +
  geom_ribbon(aes(ymin=CI_low, ymax=CI_high, fill=Intervention), alpha=0.2) +
  geom_line(aes(colour=Intervention)) +
  labs(y="MIST COVID (% Correct Pre-test)", x="Political Identification")
```


## self-identified political ideology (independent/predictor) & MIST COVID (dprime Pre-test) (dependent/outcome)

```{r}
m <- lm(MIST_dprime_Pretest_covid ~ Intervention/poly(Political_LiberalConservative, 2), 
        data=filter(df, !is.na(Political_LiberalConservative)))

display(parameters(m))

estimate_relation(m, length=30) |> 
  ggplot(aes(x=Political_LiberalConservative, y=Predicted)) +
  # geom_jitter(data=filter(df, !is.na(Political_LiberalConservative)), 
  #             aes(y=MIST_correct_Pretest_covid), alpha=0.2, size=3) +
  geom_ribbon(aes(ymin=CI_low, ymax=CI_high, fill=Intervention), alpha=0.2) +
  geom_line(aes(colour=Intervention)) +
  labs(y="MIST COVID (dprime Pre-test)", x="Political Identification")
```


## self-identified political ideology (independent/predictor) & MIST General (% Correct Pre-test) (dependent/outcome)

```{r}
m <- lm(MIST_correct_Pretest_general ~ Intervention/poly(Political_LiberalConservative, 2), 
        data=filter(df, !is.na(Political_LiberalConservative)))

display(parameters(m))

estimate_relation(m, length=30) |> 
  ggplot(aes(x=Political_LiberalConservative, y=Predicted)) +
  # geom_jitter(data=filter(df, !is.na(Political_LiberalConservative)), 
  #             aes(y=MIST_correct_Pretest_covid), alpha=0.2, size=3) +
  geom_ribbon(aes(ymin=CI_low, ymax=CI_high, fill=Intervention), alpha=0.2) +
  geom_line(aes(colour=Intervention)) +
  labs(y="MIST General (% Correct Pre-test)", x="Political Identification")
```


## self-identified political ideology (independent/predictor) & MIST General (dprime Pre-test) (dependent/outcome)

```{r}
m <- lm(MIST_dprime_Pretest_general ~ Intervention/poly(Political_LiberalConservative, 2), 
        data=filter(df, !is.na(Political_LiberalConservative)))

display(parameters(m))

estimate_relation(m, length=30) |> 
  ggplot(aes(x=Political_LiberalConservative, y=Predicted)) +
  # geom_jitter(data=filter(df, !is.na(Political_LiberalConservative)), 
  #             aes(y=MIST_correct_Pretest_covid), alpha=0.2, size=3) +
  geom_ribbon(aes(ymin=CI_low, ymax=CI_high, fill=Intervention), alpha=0.2) +
  geom_line(aes(colour=Intervention)) +
  labs(y="MIST General (dprime Pre-test)", x="Political Identification")
```


## self-identified political ideology (independent/predictor) & MIST General (% Correct difference Post-Pre) (dependent/outcome)

```{r}
m <- lm(MIST_correct_Diff_general ~ Intervention/poly(Political_LiberalConservative, 2), 
        data=filter(df, !is.na(Political_LiberalConservative)))

display(parameters(m))

estimate_relation(m, length=30) |> 
  ggplot(aes(x=Political_LiberalConservative, y=Predicted)) +
  # geom_jitter(data=filter(df, !is.na(Political_LiberalConservative)), 
  #             aes(y=MIST_correct_Pretest_covid), alpha=0.2, size=3) +
  geom_ribbon(aes(ymin=CI_low, ymax=CI_high, fill=Intervention), alpha=0.2) +
  geom_line(aes(colour=Intervention)) +
  labs(y="MIST General (% Correct difference Post-Pre)", x="Political Identification")
```


## self-identified political ideology (independent/predictor) & MIST General (dprime difference Post-Pre) (dependent/outcome)

```{r}
m <- lm(MIST_dprime_Diff_general ~ Intervention/poly(Political_LiberalConservative, 2), 
        data=filter(df, !is.na(Political_LiberalConservative)))

display(parameters(m))

estimate_relation(m, length=30) |> 
  ggplot(aes(x=Political_LiberalConservative, y=Predicted)) +
  # geom_jitter(data=filter(df, !is.na(Political_LiberalConservative)), 
  #             aes(y=MIST_correct_Pretest_covid), alpha=0.2, size=3) +
  geom_ribbon(aes(ymin=CI_low, ymax=CI_high, fill=Intervention), alpha=0.2) +
  geom_line(aes(colour=Intervention)) +
  labs(y="MIST General (dprime difference Post-Pre)", x="Political Identification")
```


## self-identified political ideology (independent/predictor) & MIST COVID (% Correct difference Post-Pre) (dependent/outcome)

```{r}
m <- lm(MIST_correct_Diff_covid ~ Intervention/poly(Political_LiberalConservative, 2), 
        data=filter(df, !is.na(Political_LiberalConservative)))

display(parameters(m))

estimate_relation(m, length=30) |> 
  ggplot(aes(x=Political_LiberalConservative, y=Predicted)) +
  # geom_jitter(data=filter(df, !is.na(Political_LiberalConservative)), 
  #             aes(y=MIST_correct_Pretest_covid), alpha=0.2, size=3) +
  geom_ribbon(aes(ymin=CI_low, ymax=CI_high, fill=Intervention), alpha=0.2) +
  geom_line(aes(colour=Intervention)) +
  labs(y="MIST COVID (% Correct difference Post-Pre)", x="Political Identification")
```


## self-identified political ideology (independent/predictor) & MIST COVID (dprime difference Post-Pre) (dependent/outcome)

```{r}
m <- lm(MIST_dprime_Diff_covid ~ Intervention/poly(Political_LiberalConservative, 2), 
        data=filter(df, !is.na(Political_LiberalConservative)))

display(parameters(m))

estimate_relation(m, length=30) |> 
  ggplot(aes(x=Political_LiberalConservative, y=Predicted)) +
  # geom_jitter(data=filter(df, !is.na(Political_LiberalConservative)), 
  #             aes(y=MIST_correct_Pretest_covid), alpha=0.2, size=3) +
  geom_ribbon(aes(ymin=CI_low, ymax=CI_high,fill=Intervention), alpha=0.2) +
  geom_line(aes(colour=Intervention)) +
  labs(y="MIST COVID (dprime difference Post-Pre)", x="Political Identification")
```


## self-identified political ideology (independent/predictor) & MIST TOTAL (% Correct difference Post-Pre) (dependent/outcome)

```{r}
m <- lm(MIST_correct_Diff ~ Intervention/poly(Political_LiberalConservative, 2), 
        data=filter(df, !is.na(Political_LiberalConservative)))

display(parameters(m))

estimate_relation(m, length=30) |> 
  ggplot(aes(x=Political_LiberalConservative, y=Predicted)) +
  # geom_jitter(data=filter(df, !is.na(Political_LiberalConservative)), 
  #             aes(y=MIST_correct_Pretest_covid), alpha=0.2, size=3) +
  geom_ribbon(aes(ymin=CI_low, ymax=CI_high, fill=Intervention), alpha=0.2) +
  geom_line(aes(color=Intervention)) +
  labs(y="MIST TOTAL (% Correct difference Post-Pre)", x="Political Identification")
```

## self-identified political ideology (independent/predictor) & MIST TOTAL (dprime difference Post-Pre) (dependent/outcome)

```{r}
m <- lm(MIST_dprime_Diff ~ Intervention/poly(Political_LiberalConservative, 2), 
        data=filter(df, !is.na(Political_LiberalConservative)))

display(parameters(m))

estimate_relation(m, length=30) |> 
  ggplot(aes(x=Political_LiberalConservative, y=Predicted)) +
  # geom_jitter(data=filter(df, !is.na(Political_LiberalConservative)), 
  #             aes(y=MIST_correct_Pretest_covid), alpha=0.2, size=3) +
  geom_ribbon(aes(ymin=CI_low, ymax=CI_high, fill=Intervention), alpha=0.2) +
  geom_line(aes(color=Intervention)) +
  labs(y="MIST TOTAL (dprime difference Post-Pre)", x="Political Identification")
```

# Political ideology and MOCRI

## self-identified political ideology (independent/predictor) & MOCRI Pre-test correct (dependent/outcome)

```{r}
m <- lm(MOCRI_correct_Pre ~ Intervention/poly(Political_LiberalConservative, 2), 
        data=filter(df, !is.na(Political_LiberalConservative)))

display(parameters(m))

estimate_relation(m, length=30) |> 
  ggplot(aes(x=Political_LiberalConservative, y=Predicted)) +
  # geom_jitter(data=filter(df, !is.na(Political_LiberalConservative)), 
  #             aes(y=MIST_correct_Pretest_covid), alpha=0.2, size=3) +
  geom_ribbon(aes(ymin=CI_low, ymax=CI_high, fill=Intervention), alpha=0.2) +
  geom_line(aes(color=Intervention)) +
  labs(y="MOCRI correct pre-test", x="Political Identification")
```


## self-identified political ideology (independent/predictor) & MOCRI Pre-test dprime (dependent/outcome)

```{r}
m <- lm(MOCRI_dprime_Pre ~ Intervention/poly(Political_LiberalConservative, 2), 
        data=filter(df, !is.na(Political_LiberalConservative)))

display(parameters(m))

estimate_relation(m, length=30) |> 
  ggplot(aes(x=Political_LiberalConservative, y=Predicted)) +
  # geom_jitter(data=filter(df, !is.na(Political_LiberalConservative)), 
  #             aes(y=MIST_correct_Pretest_covid), alpha=0.2, size=3) +
  geom_ribbon(aes(ymin=CI_low, ymax=CI_high, fill=Intervention), alpha=0.2) +
  geom_line(aes(color=Intervention)) +
  labs(y="MOCRI dprime pre-test", x="Political Identification")
```


## self-identified political ideology (independent/predictor) & MOCRI difference dprime post-pre (dependent/outcome)

```{r}
m <- lm(MOCRI_dprime_Diff ~ Intervention/poly(Political_LiberalConservative, 2), 
        data=filter(df, !is.na(Political_LiberalConservative)))

display(parameters(m))

estimate_relation(m, length=30) |> 
  ggplot(aes(x=Political_LiberalConservative, y=Predicted)) +
  # geom_jitter(data=filter(df, !is.na(Political_LiberalConservative)), 
  #             aes(y=MIST_correct_Pretest_covid), alpha=0.2, size=3) +
  geom_ribbon(aes(ymin=CI_low, ymax=CI_high,fill=Intervention), alpha=0.2) +
  geom_line(aes(color=Intervention)) +
  labs(y="MOCRI dprime difference post-pre", x="Political Identification")
```

## self-identified political ideology (independent/predictor) & MOCRI difference correct post-pre (dependent/outcome)

```{r}
m <- lm(MOCRI_correct_Diff ~ Intervention/poly(Political_LiberalConservative, 2), 
        data=filter(df, !is.na(Political_LiberalConservative)))

display(parameters(m))

estimate_relation(m, length=30) |> 
  ggplot(aes(x=Political_LiberalConservative, y=Predicted)) +
  # geom_jitter(data=filter(df, !is.na(Political_LiberalConservative)), 
  #             aes(y=MIST_correct_Pretest_covid), alpha=0.2, size=3) +
  geom_ribbon(aes(ymin=CI_low, ymax=CI_high, fill=Intervention), alpha=0.2) +
  geom_line(aes(colour=Intervention)) +
  labs(y="MOCRI correct difference post-pre", x="Political Identification")
```

:::